Tina Paper In Development

### 2024-10-06 docs/writing/paper.tex
Adding the beginnings of a diagram to show overlapping images and image focusing

\subsection{Software Design}
Software design here.

>>>>

\subsection{Software Design}
All software was written in Python VERSION and a variety of packages for the GUI, image stitching, and calculations (Should I include all the packages in writing?). Care was taken to segment the
software design into abstracted object oriented code.

\subsubsection{Graphical User Interface}
The GUI to control the machine launches from a Python script. Included are a viewer to see the live stream from the camera, buttons to jog the machine throughout the XYZ coordinate system,
setting the size of samples, and running the process to capture and stitch images. The system was designed to allow for multiple samples to be prepared in a queue for bulk digitization.

\subsubsection{Sample Digitization}
The digitization of a sample can be reduced to a few processes - capturing a grid of overlapping images, image focusing, and image stitching.
